---
title: "Care shift tracker for Neighbourhoods"
title-slide-attributes: 
  data-background-color: "#f9bf07"
  data-background-image: 'https://raw.githubusercontent.com/The-Strategy-Unit/assets/main/logo_black.svg'
  data-background-size: 10%
  data-background-position: 98% 2%
subtitle: "NNHIP community of practice, 4th March 2026"
author: "Andy Hood, Analytics Manager"
format:
  revealjs:
    slide-number: c/t
    preview-links: true
    width: 1600
    height: 900
editor: source
toc: true
toc-title: "Table of contents"
---

```{r setup}
#| echo: false

setwd("C:/Users/andrewhood/OneDrive - NHS/NHIP/left shift/git_repo/care_shift_tracker/")
library(targets)
library(quarto)
library(tidyverse)
library(gt)

```

## Introduction

- Me & team\
- The project in context\
- Today session (awareness and user feedback)

## TL;DR

- The concept is difficult to describe and measure\
- The data is often poor\
- Difficult to derive insights i.e. causal impacts\
- We've given it a good go\
- **System dynamics** and **simulation** likely a better analytical play\
- **Infrastructure** will be critical to facilitating any shifts in care [OPINION]

## Care shift concept

NHP -> TPMA -> Dynamic systems etc...

Trying to measure the shift:

- Generic versus condition/population focus?\
- Whole system versus components?\
- Commissioner versus Locality versus Delivery?

## Indicators and themes

```{r indicators}
readxl::read_excel("C:/Users/andrewhood/OneDrive - NHS/NHIP/left shift/indicators_short_list.xlsx")|>
  gt()
```

## The tracker tool

- Shiny interface\
- Multiple lenses\
- Multiple levels of interest

## Limitations & Caveats

- Partial coverage of the shift concept\
- Still a collection of silo'd views\
- Data quality and consistency away from acute sector\
- Some data gymnastics to align indicators at the 3 levels

## Walk-through

::: {.fragment fragment-index="1"}
```{=html}
<iframe src="https://www.bbc.co.uk/news" title="Care Tracker Tool" width="1600" height="850"></iframe>
```
:::

## The what next?

- Developing tool interface and visuals further?\
  - Is the content right?
  - Are the visuals alright?
  - Is there sufficient explanation?\
- Utilising more system-wide data (social care, primary care?)\
- Links to evidence of impact/improvement\
- Concepts applied to different pathways/population sub groups?\
- Feed into system dynamics model and simulations


